Model-based variable selection for regression with highly correlated variables.

### 2014-08-22 www/article.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@813 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

We used \textsc{Rmixmod} \cite{remi:hal-00919486} to estimate the Gaussian mixture densities of each covariate $\boldsymbol{X}$, settings being using at default values both for parameter and the number of components estimation. For each configuration, the {\sc mcmc} walk was launched on $10$ initial structures with 1~000 iterations each time. All the results are provided by the {\sc CorReg} package available on the {\sc cran}\footnote{http://cran.r-project.org/web/packages/CorReg/index.html}.

>>>>

We used \textsc{Rmixmod} \cite{remi:hal-00919486} to estimate the Gaussian mixture densities of each covariate $\boldsymbol{X}$, settings being used at default values both for parameter and the number of components estimation. For each configuration, the {\sc mcmc} walk was launched on $10$ initial structures with 1~000 iterations each time. All the results are provided by the {\sc CorReg} package available on the {\sc cran}\footnote{http://cran.r-project.org/web/packages/CorReg/index.html}.
